Analysis

### 2023-06-20 Analysis.rmd
sort code, add numbered figures

# Figure 1: Predictive performance across horizons (summary)
================================================================================

plot_performance <- function(scores) {
  df <- scores |>
    filter(scale %in% c("log", "natural")) |>
    summarise_scores(by = c("horizon", "model", 
                            "target_type", "scale", "type_and_scale")) |>
    rename("Dispersion" = dispersion, 
           "Overprediction" = overprediction, 
           "Underprediction" = underprediction, 
           Model = model) |>
    pivot_longer(names_to = "WIS components",
                 cols = c(`Dispersion`, `Overprediction`, `Underprediction`)) |>
    mutate(`WIS components` = fct_relevel(`WIS components`, 
                                          c("Dispersion", "Underprediction", 
                                            "Overprediction")))

@@

ggsave("output/figures/performance.png", plot = p_performance, 
       width = 7, height = 6)
```

# Figure 2: Ranks for different models
================================================================================

p_ranks <- ranks |>
  mutate(model = factor(model, levels = rev(levels(models_non_human)))) |>
  plot_ranks()
ggsave("output/figures/performance-ranks.png", 
       plot = p_ranks, 
       width = 7, height = 3.4)

@@

ggsave("output/figures/scores-and-forecasts.png", plot = p_scores_and_pred, 
       width = 9, height = 9)
```

# Figure 4: Comparison performance direct vs. Rt
================================================================================

@@

ggsave("output/figures/comparison-direct-rt-individual.png", 
       plot = p_comparison_direct_rt_individual, 
       width = 7, height = 4)

@@

@@

# Figure SI.1: Number of forecasters across the study period
================================================================================
- Figure SI.1
- numbers of forecasters used in the text

# number of experts and non-experts who used Rt forecasts
nums |>
  group_by(forecast_date, target_type, expert, method) |>
  summarise(n = n()) |>
  group_by(target_type, expert, method) |>
  summarise(
    mean = mean(`n`), 
    median = median(`n`), 
    min = min(`n`), 
    max = max(`n`)
  )
exp_method

ggsave("output/figures/num-forecasters.png", plot = p_nums, 
       width = 7, height = 5)

# forecasts |> 
#   update_expert_status() |>
#   mutate(expert = ifelse(expert, "Expert", "Non-Expert")) |>
#   filter(forecast_date == "2021-06-07", 
#          model %in% models_human, horizon == 1, 
#          quantile == 0.5) |> 
#   mutate(method = ifelse(grepl("(Rt)", model), "Rt", "direct")) |>
#   mutate(model = gsub("\ \\(Rt\\)", "", model)) |> 
#   group_by(target_type, method, expert) |> 
#   summarise(n = length(unique(model)))

@@

# Figure SI.5: Performance of "experts" and "non-experts"
================================================================================
Separate ensemble of experts and non-experts

p_scores_expert <- plot_performance(expert_ensemble$scores)
ggsave("output/figures/performance-expert.png", 
       plot = p_scores_expert, 
       width = 7, height = 6)

>>>>

# Figure 1: Number of forecasters across the study period
================================================================================
- numbers of forecasters used in the text

# number of experts and non-experts who used Rt forecasts
nums |>
  group_by(forecast_date, target_type, expert, method) |>
  summarise(n = n()) |>
  group_by(target_type, expert, method) |>
  summarise(
    mean = mean(`n`), 
    median = median(`n`), 
    min = min(`n`), 
    max = max(`n`)
  )

ggsave("output/figures/num-forecasters.png", plot = p_nums, 
       width = 7, height = 5)
ggsave("output/figures/Figure-1.png", plot = p_nums, 
       width = 7, height = 5)

forecasts |>
  update_expert_status() |>
  mutate(expert = ifelse(expert, "Expert", "Non-Expert")) |>
  filter(forecast_date == "2021-06-07",
         model %in% models_human, horizon == 1,
         quantile == 0.5) |>
  mutate(method = ifelse(grepl("(Rt)", model), "Rt", "direct")) |>
  mutate(model = gsub("\ \\(Rt\\)", "", model)) |>
  group_by(target_type, method, expert) |>
  summarise(n = length(unique(model)))

# Figure 2: Predictive performance across horizons (summary)
================================================================================

```{r}
plot_performance <- function(scores) {
  df <- scores |>
    filter(scale %in% c("log", "natural")) |>
    summarise_scores(by = c("horizon", "model", 
                            "target_type", "scale", "type_and_scale")) |>
    rename("Dispersion" = dispersion, 
           "Overprediction" = overprediction, 
           "Underprediction" = underprediction, 
           Model = model) |>
    pivot_longer(names_to = "WIS components",
                 cols = c(`Dispersion`, `Overprediction`, `Underprediction`)) |>
    mutate(`WIS components` = fct_relevel(`WIS components`, 
                                          c("Dispersion", "Underprediction", 
                                            "Overprediction")))

@@

ggsave("output/figures/performance.png", plot = p_performance, 
       width = 7, height = 6)
ggsave("output/figures/Figure-2.png", plot = p_performance, 
       width = 7, height = 6)

@@

ggsave("output/figures/scores-and-forecasts.png", plot = p_scores_and_pred, 
       width = 9, height = 9)
ggsave("output/figures/Figure-3.png", plot = p_scores_and_pred, 
       width = 9, height = 9)
```

# Figure 4: Ranks for different models
================================================================================

p_ranks <- ranks |>
  mutate(model = factor(model, levels = rev(levels(models_non_human)))) |>
  plot_ranks()
ggsave("output/figures/performance-ranks.png", 
       plot = p_ranks, 
       width = 7, height = 3.4)
ggsave("output/figures/Figure-4.png", 
       plot = p_ranks, 
       width = 7, height = 3.4)

# Figure 5: Comparison performance direct vs. Rt
================================================================================

@@

ggsave("output/figures/comparison-direct-rt-individual.png", 
       plot = p_comparison_direct_rt_individual, 
       width = 7, height = 4)
ggsave("output/figures/Figure-5.png", 
       plot = p_comparison_direct_rt_individual, 
       width = 7, height = 4)

@@

# Figure 6: Performance of "experts" and "non-experts"
================================================================================
Separate ensemble of experts and non-experts

p_scores_expert <- plot_performance(expert_ensemble$scores)
ggsave("output/figures/performance-expert.png", 
       plot = p_scores_expert, 
       width = 7, height = 6)
ggsave("output/figures/Figure-6.png", 
       plot = p_scores_expert, 
       width = 7, height = 6)

@@

@@
